---
title: "DATA 606 Project Proposal"
author: "Liam Byrne"
date: "October 16, 2016"
output: pdf_document
---

```{r include=FALSE, cache=FALSE}
# DO NOT REMOVE
# THIS IS FOR SETTING SOME PLOTTING PARAMETERS SO THAT YOUR PLOTS DON'T TAKE UP TOO MUCH SPACE
# IF YOU WOULD LIKE TO CHANGE THESE, SEE HELP FILES ON THE par() FUNCTION
# OR ASK FOR HELP
library(knitr)
library("tidyr")
library("dplyr")
## set global chunk options
opts_chunk$set(fig.path='figure/manual-', cache.path='cache/manual-', fig.align='center', fig.show='hold', par=TRUE)
## tune details of base graphics (http://yihui.name/knitr/hooks)
knit_hooks$set(par=function(before, options, envir){
if (before && options$fig.show!='none') par(mar=c(4,4,.2,.1),cex.lab=.95,cex.axis=.9,mgp=c(2,.7,0),tcl=-.3)
})
```

```{r loadData}
file_link <- 
  "https://raw.githubusercontent.com/Liam-O/Project/master/worldBankProfile.csv"

# Returns a data table
worldbank  <- fread(file_link, header = TRUE, na.strings = c("", ".."), data.table = TRUE, nrows = 13861)

worldbank <-worldbank %>%
    gather(year, figure, 6:8) %>%
    select(c(1,3, 6, 7)) %>%
    spread('Series Name', figure) %>%
    arrange('Country Name')

knitr::kable(head(worldbank))

```


### Research question 

**You should phrase your research question in a way that matches up with the scope of inference your dataset allows for.**



### Cases 
```{r}
unique(as.factor(worldbank$`Country Name`))
```

**What are the cases, and how many are there?**



### Data collection 

**Describe the method of data collection.**



### Type of study 

**What type of study is this (observational/experiment)?**



### Data Source 

**If you collected the data, state self-collected. If not, provide a citation/link.**




### Response 

**What is the response variable, and what type is it (numerical/categorical)?**



### Explanatory 

**What is the explanatory variable, and what type is it (numerical/categorival)?**



### Relevant summary statistics 

**Provide summary statistics relevant to your research question. For example, if you're comparing means across groups provide means, SDs, sample sizes of each group. This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**

```{r}

```
