---
title: "DATA 606 Project Proposal"
author: "Liam Byrne"
date: "October 16, 2016"
output: pdf_document
---

```{r include=FALSE, cache=FALSE}
# DO NOT REMOVE
# THIS IS FOR SETTING SOME PLOTTING PARAMETERS SO THAT YOUR PLOTS DON'T TAKE UP TOO MUCH SPACE
# IF YOU WOULD LIKE TO CHANGE THESE, SEE HELP FILES ON THE par() FUNCTION
# OR ASK FOR HELP
library("knitr")
library("tidyr")
library("dplyr")
library("data.table")
library("ggplot2")
## set global chunk options
opts_chunk$set(fig.path='figure/manual-', cache.path='cache/manual-', fig.align='center', fig.show='hold', par=TRUE)
## tune details of base graphics (http://yihui.name/knitr/hooks)
knit_hooks$set(par=function(before, options, envir){
if (before && options$fig.show!='none') par(mar=c(4,4,.2,.1),cex.lab=.95,cex.axis=.9,mgp=c(2,.7,0),tcl=-.3)
})
```

Loading data. Data dictionary available [here](https://github.com/Liam-O/Project/blob/master/worldbankDict.csv)

```{r loadData}
file_link <- 
  "https://raw.githubusercontent.com/Liam-O/Project/master/worldBankProfile.csv"

# Returns a data table
worldbank  <- fread(file_link,
                    header = TRUE,
                    na.strings = c("", ".."),
                    data.table = TRUE,
                    nrows = 13861)

worldbank <-worldbank %>%
    gather(year, figure, 6:8) %>%
    select(c(1,3, 6, 7)) %>%
    spread('Series Name', figure)

#Will clean headers later

```

### Research question
The project will look at GDP growth for all respective countries provided by [The World Country Profiles dataset](http://data.worldbank.org/data-catalog/country-profiles) and possible mitigating factors leading to negative or postie growth


### Cases 
Every existing country is a case. There are `r length(unique(as.factor(worldbank[,1])))` in the set.


### Data collection 

The data was gathered from the [The World Country Profiles dataset](http://data.worldbank.org/data-catalog/country-profiles)


### Type of study 

The data in `worldbank` deals with historical data for 1990, 2000 and 2015. The study will, thus, be observation.


### Data Source 

The data was gathered from the [The World Country Profiles dataset](http://data.worldbank.org/data-catalog/country-profiles)


### Response 

The response variable will be GDP in a $US conversion, so numerical.

### Explanatory 

The explanatory variable has not been decided upon yet. There are 59 possible explanatory variables in the data set. Some could include:

* Credit provided by financial sector
* Fresh water availability
* Urban growth
* Purchasing power
* School enrollment

### Relevant summary statistics 

**Provide summary statistics relevant to your research question. For example, if you're comparing means across groups provide means, SDs, sample sizes of each group. This step requires the use of R, hence a code chunk is provided below. Insert more code chunks as needed.**

```{r, warning = FALSE}
summary(worldbank$`GDP (current US$)`)
ggplot(worldbank, aes(`GDP (current US$)`)) + geom_histogram() +  scale_x_log10()
```

The GDP data is heavily skewed to the right, but it is generally normalized by a log transform.